\documentclass{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{hyperref}

\title{Proposal Submission for Deep Learning Project}
\author{
    Group Members: \\
    Farooq Mahmud
}
\date{}

\begin{document}

\maketitle

\section{Introduction}
For my deep learning project, I will analyze and replicate the seminal deep learning paper, \textit{"Going Deeper with Convolutions"} by Christian Szegedy et al., presented at the CVPR 2015 conference. This paper introduces the Inception architecture, which revolutionized deep learning by addressing the challenge of building efficient and scalable neural networks.

The primary aim of this project is to implement the \textit{GoogLeNet} architecture described in the paper using TensorFlow, replicate its performance on the ImageNet dataset, and evaluate its generalization capability by applying it to the \textit{CIFAR-10} dataset. Additionally, I will provide a critical analysis of the impact of the Inception architecture on the field of deep learning, highlighting its influence on subsequent research and applications.

\section{Objectives}
The key objectives of our project are as follows:
\begin{itemize}
    \item \textbf{Understand and articulate} the core ideas and contributions of the paper, including the use of Inception modules for building efficient and scalable neural networks.
    \item \textbf{Implement the GoogLeNet architecture} using TensorFlow and train the model on the ImageNet dataset (or a subset thereof).
    \item \textbf{Replicate the results} reported in the paper, including the model's classification performance on ImageNet.
    \item \textbf{Generalize the model} by applying it to the CIFAR-10 dataset and evaluate its performance on this smaller dataset.
    \item \textbf{Analyze the paper's impact} on deep learning, particularly in computer vision, by reviewing citations and subsequent research that built on this work.
    \item \textbf{Document the challenges} encountered during implementation, training, and testing.
\end{itemize}

\end{document}
